\iffalse
\noindent In recent years, major advances have been made in 3D scene reconstruction, with a number of approaches now able to yield dense, globally-consistent models at scale. However, much less progress has been made for objects, which can exhibit far fewer unambiguous geometric/texture cues than a full scene, and thus be much harder to track against. Recently, robust, globally-consistent scene reconstruction has been achieved by combining a multi-segment representation with loop closure detection and an online model correction algorithm. The multi-segment approach naturally reduces drift, and the correction algorithm further refines the resulting model. In this paper, we show how to extend this approach to reconstruct accurate, globally-consistent object models. Central to our approach is a novel, probabilistic fusion framework that we use to separate the object of interest from the surrounding scene. We perform both qualitative and quantitative experiments to compare our approach to the current state-of-the-art, and demonstrate compelling improvements in both pose estimation and model quality.
\fi

In recent years, major advances have been made in 3D scene reconstruction, with a number of approaches now able to yield dense, globally-consistent models at scale. However, much less progress has been made for objects, which can exhibit far fewer unambiguous geometric/texture cues than a full scene, and thus be much harder to track against.
In this work we present a novel probabilistic object reconstruction framework that simultaneously allows for online, implicit deformation of the objects surface to reduce tracking drift and handle 
loop closure events. Coupled with our probabilistic formulation is the use of a multi subsegment representation of the object, used to enforce global global consistency, with segmentation of the object 
built in to the formulation. Finally, we employ a CRF framework to refine the overall segmentation, defined by a probability field over the object. We present compelling results over the current state-of-the-art 
object reconstruction work and demonstrate robustness and consistency w.r.t. established dense SLAM frameworks.